White Wine Quality
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(dplyr)
library(memisc)
library(scales)
library(tidyr)
library(ggthemes)
library(gridExtra)
library(reshape2)
library(GGally)
library(RColorBrewer)
```
# Introduction
This dataset was created, using white wine samples.

The inputs include objective tests (e.g. PH values) and the output is based on sensory data (median of at least 3 evaluations made by wine experts). Each expert graded the wine quality between 0 (very bad) and 10 (very excellent).

Input variables (based on physicochemical tests):

1.   fixed acidity (tartaric acid - g / dm^3)
2.   volatile acidity (acetic acid - g / dm^3)
3.   citric acid (g / dm^3)
4.   residual sugar (g / dm^3)
5.   chlorides (sodium chloride - g / dm^3
6.   free sulfur dioxide (mg / dm^3)
7.   total sulfur dioxide (mg / dm^3)
8.   density (g / cm^3)
9.   pH
10.   sulphates (potassium sulphate - g / dm3)
11.   alcohol (% by volume)

Output variable (based on sensory data):

12.   quality (score between 0 and 10)

If you need to know more information about the data [click here](https://s3.amazonaws.com/udacity-hosted-downloads/ud651/wineQualityInfo.txt).

```{r echo=FALSE, Load_the_Data}
# Load the Data
whitewine <- read.csv('wineQualityWhites.csv')
str(whitewine)
```
I notice that all variables are quantitative then we can get better relationship to get the varibles are change the value of quality.


# Univariate Plots Section

> **Tip**: In this section, you should perform some preliminary exploration of
your dataset. Run some summaries of the data and create univariate plots to
understand the structure of the individual variables in your dataset. Don't
forget to add a comment after each plot or closely-related group of plots!
There should be multiple code chunks and text sections; the first one below is
just to help you get started.

I will Explore quality variablbe to know the distribution of it.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= quality), data = whitewine)+
  geom_histogram()
```
```{r echo=FALSE,message= FALSE , warning= FALSE}
summary(whitewine$quality)
```

I improve the graph to get better comment for this graph by make breaks for the x scale and change the bin width becase this varibale have range between 6 intgers numbers.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= quality), data = whitewine)+
  geom_histogram(binwidth = 1)+
  scale_x_continuous(breaks = seq(3,9,1))
```

More than 2300 wines have guality grade equal 6 and more than 1400 wines have quality grade equal 5 then the nearly of 2800 wines have normal or good reaction for expert and less than 1250 wines have guality grade greater than 6, I will explore variables that help me to understand of distribution of variables.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= fixed.acidity), data = whitewine)+
  geom_histogram()
```

Most of wine have fixed acidity between 5.5 and 8, some variable are outlier values at 12, 14.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= volatile.acidity), data = whitewine)+
  geom_histogram()
```
```{r echo=FALSE,message= FALSE , warning= FALSE}
summary(whitewine$volatile.acidity)
```

Most of wines have volatile.acitdity between 0.15 and .45 and some wines are outliers greater than 0.9.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= citric.acid), data = whitewine)+
  geom_histogram()
```
```{r echo = FALSE, message=FALSE, warning= FALSE}
summary(whitewine$citric.acid)
```

Greater peak in the plot and most of wine have citric acid between 0.25 and 0.4.


```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= pH), data = whitewine)+
  geom_histogram()
```
```{r echo=FALSE,message= FALSE , warning= FALSE}
summary(whitewine$pH)
```

Most of wines have pH value between 3 and 3.3.


```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= residual.sugar), data = whitewine)+
  geom_histogram()
```

The graph is skewed right and I'll apply log function to understand the distribution of the variable.
```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= residual.sugar), data = whitewine)+
  geom_histogram()+
  scale_x_log10()
```
```{r echo=FALSE,message= FALSE , warning= FALSE}
summary(whitewine$residual.sugar)
```

I notice the wines are in two group of residual sugar and some values are outliers.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= density), data = whitewine)+
  geom_histogram()
```
```{r echo=FALSE,message= FALSE , warning= FALSE}
summary(whitewine$density)
```

The almost of the wines have denisty between 0.98 to 1 and some outliers are larger than 1.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= density), data = whitewine)+
  geom_histogram()+
  coord_cartesian(xlim = c(0.985, 1))
```

I think that the density don't extremly control on the grade of quality because almost of wines have nearly value of density.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= chlorides), data = whitewine)+
  geom_histogram()
```
```{r echo=FALSE,message= FALSE , warning= FALSE}
summary(whitewine$chlorides)
```

The almost of wines have value of chlorides between 0 and 0.1, and I think that chlorides don't have extremly control on quality grade.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= sulphates), data = whitewine)+
  geom_histogram()
```
```{r echo=FALSE,message= FALSE , warning= FALSE}
summary(whitewine$sulphates)
```

Most of wines have sulphates values between 0.35 and 0.6 and some values are outliers.

```{r echo = FALSE, message= FALSE, warning = FALSE}
ggplot(aes(x = alcohol), data = whitewine)+
  geom_histogram()+
  scale_x_continuous(breaks = seq(7, 15,1))
```
```{r echo = FALSE, message=FALSE, warning=FALSE}
summary(whitewine$alcohol)
```
Most of wines alcohol value between 9 and 11.5 and I think that alcohol predicting grade of the wine quality.

# Univariate Analysis

> **Tip**: Now that you've completed your univariate explorations, it's time to
reflect on and summarize what you've found. Use the questions below to help you
gather your observations and add your own if you have other thoughts!

### What is the structure of your dataset?
There are 4,898 wines in the dataset with 12 features (fixed.acidity, volatile.acidity,
citric.acid, residual.sugar, chlorides, free.sulfur.dioxide, total.sulfur.dioxide, density, pH, sulphates, alcohol, quality).

other observations:

* About 75% of wines have quality grade less than 6.
* The median pH for white wines is 3.18 and the max pH 3.82.
* The median sulphates for white wines is 0.47.
* About 75% of wines have alcohol less tnan 11.40 and the max value equal 14.2.

### What is/are the main feature(s) of interest in your dataset?
The main feature in the data set are alcohol and quality. I'd like to determine which features are best for predicting the price of a diamonds. I suspect alcohol and some combination of the other variables can be used to build a predictive model to quality of wines.
### What other features in the dataset do you think will help support your \
fixed acidity, volatile acidity, citric acid, residual sugar, chlorides, free sulfur dioxide, total sulfur dioxide, density, pH,and sulphates. I think alcohol, pH,and sulphates probably contibute most to the quality after make rsearching.

### Did you create any new variables from existing variables in the dataset?
No
### Of the features you investigated, were there any unusual distributions? \Did you perform any operations on the data to tidy, adjust, or change the form \of the data? If so, why did you do this?
I log-transformed the right skewed residual.sugar distributions. The tranformed distribution for price appears bimodal with the price peaking around 2 or so and again around 10.

# Bivariate Plots Section

> **Tip**: Based on what you saw in the univariate plots, what relationships
between variables might be interesting to look at in this section? Don't limit
yourself to relationships between a main output feature and one of the
supporting variables. Try to look at relationships between supporting variables
as well.

```{r echo=FALSE, Bivariate_Plots}

```

# Bivariate Analysis

> **Tip**: As before, summarize what you found in your bivariate explorations
here. Use the questions below to guide your discussion.

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

### What was the strongest relationship you found?


# Multivariate Plots Section

> **Tip**: Now it's time to put everything together. Based on what you found in
the bivariate plots section, create a few multivariate plots to investigate
more complex interactions between variables. Make sure that the plots that you
create here are justified by the plots you explored in the previous section. If
you plan on creating any mathematical models, this is the section where you
will do that.

```{r echo=FALSE, Multivariate_Plots}

```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

### Were there any interesting or surprising interactions between features?

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

# Final Plots and Summary

> **Tip**: You've done a lot of exploration and have built up an understanding
of the structure of and relationships between the variables in your dataset.
Here, you will select three plots from all of your previous exploration to
present here as a summary of some of your most interesting findings. Make sure
that you have refined your selected plots for good titling, axis labels (with
units), and good aesthetic choices (e.g. color, transparency). After each plot,
make sure you justify why you chose each plot by describing what it shows.

### Plot One
```{r echo=FALSE, Plot_One}

```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}

```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```

### Description Three

------

# Reflection

> **Tip**: Here's the final step! Reflect on the exploration you performed and
the insights you found. What were some of the struggles that you went through?
What went well? What was surprising? Make sure you include an insight into
future work that could be done with the dataset.

> **Tip**: Don't forget to remove this, and the other **Tip** sections before
saving your final work and knitting the final report!