White Wine Quality
========================================================

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(dplyr)
library(memisc)
library(scales)
library(tidyr)
library(ggthemes)
library(gridExtra)
library(reshape2)
library(GGally)
library(RColorBrewer)
```
# Introduction
This dataset was created, using white wine samples.

The inputs include objective tests (e.g. PH values) and the output is based on sensory data (median of at least 3 evaluations made by wine experts). Each expert graded the wine quality between 0 (very bad) and 10 (very excellent).

Input variables (based on physicochemical tests):

1.   fixed acidity (tartaric acid - g / dm^3)
2.   volatile acidity (acetic acid - g / dm^3)
3.   citric acid (g / dm^3)
4.   residual sugar (g / dm^3)
5.   chlorides (sodium chloride - g / dm^3
6.   free sulfur dioxide (mg / dm^3)
7.   total sulfur dioxide (mg / dm^3)
8.   density (g / cm^3)
9.   pH
10.   sulphates (potassium sulphate - g / dm3)
11.   alcohol (% by volume)

Output variable (based on sensory data):

12.   quality (score between 0 and 10)

If you need to know more information about the data [click here](https://s3.amazonaws.com/udacity-hosted-downloads/ud651/wineQualityInfo.txt).

```{r echo=FALSE, Load_the_Data}
# Load the Data
whitewine <- read.csv('wineQualityWhites.csv')
str(whitewine)
```
I notice that all variables are quantitative then we can get better relationship to get the varibles are change the value of quality.


# Univariate Plots Section

> **Tip**: In this section, you should perform some preliminary exploration of
your dataset. Run some summaries of the data and create univariate plots to
understand the structure of the individual variables in your dataset. Don't
forget to add a comment after each plot or closely-related group of plots!
There should be multiple code chunks and text sections; the first one below is
just to help you get started.

I will Explore quality variablbe to know the distribution of it.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= quality), data = whitewine)+
  geom_histogram()
```
```{r echo=FALSE,message= FALSE , warning= FALSE}
summary(whitewine$quality)
```

I improve the graph to get better comment for this graph by make breaks for the x scale and change the bin width becase this varibale have range between 6 intgers numbers.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= quality), data = whitewine)+
  geom_bar()+
  scale_x_continuous(breaks = seq(3,9,1))
```

More than 2300 wines have guality grade equal 6 and more than 1400 wines have quality grade equal 5 then the nearly of 2800 wines have normal or good reaction for expert and less than 1250 wines have guality grade greater than 6, I will explore variables that help me to understand of distribution of variables and I don't the format of the quality columns to factor because this whlie make me too diffcult to analysis it and make model becuase quality it basic variable.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= fixed.acidity), data = whitewine)+
  geom_histogram()
```

Most of wine have fixed acidity between 5.5 and 8, some variable are outlier values at 12, 14.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= volatile.acidity), data = whitewine)+
  geom_histogram()
```
```{r echo=FALSE,message= FALSE , warning= FALSE}
summary(whitewine$volatile.acidity)
```

Most of wines have volatile.acitdity between 0.15 and .45 and some wines are outliers greater than 0.9.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= total.sulfur.dioxide), data = whitewine)+
  geom_histogram()
```
```{r echo = FALSE, message=FALSE, warning= FALSE}
summary(whitewine$total.sulfur.dioxide)
```

Most of wines have total.sulfur.dioxide in range form 100 to 200 and some greater than 280 are outlier.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= pH), data = whitewine)+
  geom_histogram()
```
```{r echo=FALSE,message= FALSE , warning= FALSE}
summary(whitewine$pH)
```

Most of wines have pH value between 3 and 3.3.


```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= residual.sugar), data = whitewine)+
  geom_histogram()
```

The graph is skewed right and I'll apply log function to understand the distribution of the variable.
```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= residual.sugar), data = whitewine)+
  geom_histogram()+
  scale_x_log10()
```
```{r echo=FALSE,message= FALSE , warning= FALSE}
summary(whitewine$residual.sugar)
```

I notice the wines are in two group of residual sugar and some values are outliers.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= density), data = whitewine)+
  geom_histogram()
```
```{r echo=FALSE,message= FALSE , warning= FALSE}
summary(whitewine$density)
```

The almost of the wines have denisty between 0.98 to 1 and some outliers are larger than 1 and I'll zoom in the next graph for This region.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= density), data = whitewine)+
  geom_histogram()+
  coord_cartesian(xlim = c(0.985, 1))
```



```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= chlorides), data = whitewine)+
  geom_histogram()
```
```{r echo=FALSE,message= FALSE , warning= FALSE}
summary(whitewine$chlorides)
```

The almost of wines have value of chlorides between 0 and 0.1, and I think that chlorides don't have extremly control on quality grade.

```{r echo=FALSE,message= FALSE , warning= FALSE}
ggplot(aes(x= sulphates), data = whitewine)+
  geom_histogram()
```
```{r echo=FALSE,message= FALSE , warning= FALSE}
summary(whitewine$sulphates)
```

Most of wines have sulphates values between 0.35 and 0.6 and some values are outliers.

```{r echo = FALSE, message= FALSE, warning = FALSE}
ggplot(aes(x = alcohol), data = whitewine)+
  geom_histogram()+
  scale_x_continuous(breaks = seq(7, 15,1))
```
```{r echo = FALSE, message=FALSE, warning=FALSE}
summary(whitewine$alcohol)
```
Most of wines alcohol value between 9 and 11.5 and I think that alcohol predicting grade of the wine quality.

# Univariate Analysis

### What is the structure of your dataset?
There are 4,898 wines in the dataset with 12 features (fixed.acidity, volatile.acidity,
citric.acid, residual.sugar, chlorides, free.sulfur.dioxide, total.sulfur.dioxide, density, pH, sulphates, alcohol, quality).

other observations:

* About 75% of wines have quality grade less than 6.
* The median pH for white wines is 3.18 and the max pH 3.82.
* The median sulphates for white wines is 0.47.
* About 75% of wines have alcohol less tnan 11.40 and the max value equal 14.2.

### What is/are the main feature(s) of interest in your dataset?
The main feature in the data set are alcohol and quality. I'd like to determine which features are best for predicting the price of a diamonds. I suspect alcohol and some combination of the other variables can be used to build a predictive model to quality of wines.
### What other features in the dataset do you think will help support your \
density, residual.sugar, chlorides, and total.sulfur.dioxide. I think alcohol, density,and chlorides are probably contibute most to the quality after make rsearching.

### Did you create any new variables from existing variables in the dataset?
No
### Of the features you investigated, were there any unusual distributions? \Did you perform any operations on the data to tidy, adjust, or change the form \of the data? If so, why did you do this?
I log-transformed the right skewed residual.sugar distributions. The tranformed distribution for price appears bimodal with the price peaking around 2 or so and again around 10.

# Bivariate Plots Section

```{r echo=FALSE, message = FALSE, Bivariate_Plots}
ggpairs(whitewine[ ,2:13],axisLabels = 'internal', lowe = list(continuous = wrap("points", shape = I('.'))))
```
From the data, density, residual.sugar, chlorides, and total.sulfur.dioxide do not seem to have strong correlations with quality, but density is pretty large and residual.sugar, chlorides, and total.sulfurdioxide moderately  correlated with alcohol. I want to look closer at scatter plots involving quality and some other variables like alcohol, density and residual.sugar.
```{r echo = FALSE, message= FALSE, warning = FALSE}
ggplot(aes(x = quality, y = alcohol), data = whitewine)+
  geom_point()
```

My problem now, I can't get best relationship in this graph and overplot because the quality is integer numbers then I'll jitter point to see some imporve in relationship in points between quality and alcohol and use alpha.

```{r echo = FALSE, message= FALSE, warning = T}
ggplot(aes(x = quality, y= alcohol),data = whitewine)+
  geom_jitter(alpha = 0.2, width = 1)+
  geom_smooth(method = 'lm')
```

Notice is this pretty good relationship between alcohol and quality, as av the alcohol increases the quality increases.

>Note: Because I make jitter for points in x axis in last graph when I graph quality on x-axis then I make jitter for points in x axis for next graphs between (quality - density) and (quality - residual.sugar)

```{r echo = FALSE, message= FALSE, warning = T}
ggplot(aes(x = quality, y= density),data = whitewine)+
  geom_jitter(alpha = 0.2, width = 1)+
  geom_smooth(method = 'lm')
```

I notice a realtion with density but we have three points outliers on y-axis great than 1.005, then I remove them form next graph to see the relationship between quality and density.

```{r echo = FALSE, message= FALSE, warning = T}
ggplot(aes(x = quality, y= density),data = whitewine)+
  geom_jitter(alpha = 0.2, width = 1)+
  geom_smooth(method = 'lm')+
  coord_cartesian(ylim = c(.985, 1.005))

```
as smooth line when density increases the quality decreases.

>Note: from histogram of residual.sugar in the last section then I'll transform the residual.sugar variable by log function.

```{r echo = FALSE, message= FALSE, warning = T}
ggplot(aes(x = quality, y= residual.sugar),data = whitewine)+
  geom_jitter(alpha = 0.2, width = 1)+
  geom_smooth(method = 'lm')+
  scale_y_log10()
```

Notice that this very weak realtion ship between quality and residual.sugar.

Next: density is pretty large and residual.sugar, chlorides, and total.sulfurdioxide moderately  correlated with alcohol. I want to look closer at scatter plots involving alcohol and some other variables like density, residual.sugar, chlorides, and total.sulfurdioxide.

```{r echo = FALSE, message= FALSE, warning = T}
ggplot(aes(y = density, x= alcohol),data = whitewine)+
  geom_point()
```

I'll remove outliers on axis and solve overploting problem by transpering and jitter function.

```{r echo = FALSE, message= FALSE, warning = T}
ggplot(aes(y = density, x= alcohol),data = whitewine)+
  geom_jitter(alpha = 0.1 , width = 0.1)+
  coord_cartesian(ylim = c(0.985, 1.005))
```
 
 we don't need to put linear smooth to see the relationship between alcohol and density because it's pretty large relationship as density increases, alcohol decreases.
 
```{r echo = FALSE, message= FALSE, warning = T}
ggplot(aes(x= alcohol, y = residual.sugar),data = whitewine)+
  geom_point()
```

I'll apply log functioin to residual.sugar variable and apply jitter function and transpiring to solve problem overploting
```{r echo = FALSE, message= FALSE, warning = T}
ggplot(aes(x= alcohol, y = residual.sugar),data = whitewine)+
  geom_jitter(alpha = 0.1 , width = 0.1)+
  scale_y_log10()+
  geom_smooth(method = 'lm')
```

Smooth line is help to understand that "as the residual.sugar increases the alcohol decreases"

```{r echo = FALSE, message= FALSE, warning = T}
ggplot(aes(x= alcohol, y = chlorides),data = whitewine)+
  geom_point()
```

I'll apply log functioin to chlorides variable and apply jitter function and transpiring to solve problem overploting

```{r echo = FALSE, message= FALSE, warning = T}
ggplot(aes(x= alcohol, y = chlorides),data = whitewine)+
  geom_jitter(alpha = 0.1 , width = 0.1)+
  scale_y_log10()+
  geom_smooth(method = 'lm')
```

As chlorides increases the alcohol decreases, I notice it by liner smooth model to see this relationship 

```{r echo = FALSE, message= FALSE, warning = T}
ggplot(aes(x= alcohol, y = total.sulfur.dioxide),data = whitewine)+
  geom_point()
```

I'll remove outlier form the y-axis and solve the overploting problem

```{r echo = FALSE, message= FALSE, warning = T}
ggplot(aes(x= alcohol, y = total.sulfur.dioxide),data = whitewine)+
  geom_jitter(alpha = 0.2, width = 0.1)+
  coord_cartesian(ylim = c(0,300))+
  geom_smooth(method = 'lm')
```

As total.sulfur.dioxide increases the alcohol decreases, I notice it by liner smooth model to see this relationship 

# Bivariate Analysis


### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

The relationship between quality and alcohol because alcohol is the strongest correlated varible by quality and in the first the realtionship, it's diffcult to see because the value of records on the quality variable is integer and most of points ploting over each other, to sovle this problem I use jitter and transparing function to help me to see the relationship.

The force for this graph and relationships help me to the effect of the other variable on the qulity in multigraph.


### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

Alcohol and Chlorides , Alcohol and Residual.Sugar

Because chlorides and residual.sugar have the reverse relationship to alcohol, and chlorides is the amount of salt in the wine, and residual.sugar is the amount of sugar remaining after fermentation stops, it's rare to find wines with less than 1 gram/liter and wines with greater than 45 grams/liter are considered sweet, these not problem but every thing don't have good quality rate between people if it have more slat and more sugar.
### What was the strongest relationship you found?

between density and alcohol, I don't need to make smooth line to see the relationship.
# Multivariate Plots Section

In this section I'll add each of theses variables (density, residual.sugar, chlorides, total.sulfurdioxide.) to see reacttion for every one on quality and alcohol scatter plot after update in the bivariatte plots section.
```{r echo=FALSE, Multivariate_Plots}
ggplot(aes(x = quality, y= alcohol,color =density),data = whitewine)+
  scale_color_gradientn(colours = terrain.colors(4))+
  geom_jitter(width = 1)
  
```

Don't see much variation on Density when hold the alcohol as aconstant, we don't see any change in the color.

```{r echo=FALSE}
ggplot(aes(x = quality, y= alcohol,color =residual.sugar),data = whitewine)+
  scale_color_gradientn(colours = terrain.colors(4))+
  geom_jitter(width = 1)
  
```
perrty see variation on residual.sugar when hold the alcohol as aconstant, but don't seq. then we don't get best information on this.

```{r echo=FALSE}
ggplot(aes(x = quality, y= alcohol,color =chlorides),data = whitewine)+
  scale_color_gradientn(colours = terrain.colors(4))+
  geom_jitter(width = 1)
  
```
perrty see variation on chlorides when hold the alcohol as aconstant, but don't seq. then we don't get best information on this.

```{r echo= F}
ggplot(aes(x = quality, y= alcohol,color =total.sulfur.dioxide),data = whitewine)+
  scale_color_gradientn(colours = terrain.colors(4))+
  geom_jitter(width = 1)
```

perrty see variation on total.sulfur.dioxide when hold the alcohol as aconstant, but don't seq. then we don't get best information on this.

After I these plot I don't get any good information help to understand the variable that have storng effect on quality like alcohol and other variables have small effect we can make model to compute this effect.
```{r echo=F}
m1 <- lm(I(quality)~I(alcohol), data = whitewine)
m2 <- update( m1, ~ . + density )
m3 <- update( m2, ~ . + chlorides )
m4 <- update( m3, ~ . + residual.sugar)
m5 <- update( m4, ~ . + total.sulfur.dioxide)

mtable(m1,m2,m3,m4,m5, sdigits = 3)
```

we see from model the prove of my graphs and on my writing because the varible only have strong impact on quality grade and another three density, chlorides, and resdial.sugar they have weak impact on quality and all other variable nearly to zero impact.

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

I don't get new relationship in this section because the quality is mostly depended on the amount of alcohol.

### Were there any interesting or surprising interactions between features?

surprising because only one variabel has strong impact on grade of quality.

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

I see from model the prove of my graphs and on my writing because the varible only have strong impact on quality grade and another three density, chlorides, and resdial.sugar they have weak impact on quality and all other variable nearly to zero impact.
------

# Final Plots and Summary


### Plot One
```{r echo=FALSE, Plot_One}
ggplot(aes(x= quality), data = whitewine)+
  geom_bar(fill = '#7CFC00')+
  scale_x_continuous('Quality(score between 0 and 10)',breaks = seq(3,9,1))+
  scale_y_continuous('Count of Wines')+
  ggtitle('Quality Bar Chart')
```

### Description One
This is the bar Chart for quality variable because quality is integer data type and have only 7 values along the data, and the max number of wines have quality grade equal 6 , min number of wines have quality grade equal 9.

### Plot Two
```{r echo=FALSE, Plot_Two}
ggplot(aes(x = quality, y= alcohol),data = whitewine)+
  geom_jitter(alpha = 0.2, width = 1, fill= '#7CFC00', color = 'black',shape = 21)+
  geom_smooth(method = 'lm',color = 'black')+
  scale_y_continuous('Alcohol (% by volume)')+
  scale_x_continuous('Quality (score between 0 and 10)')+
  ggtitle('Quality by Alcohol')
```

### Description Two
Descripe the relationship between quality and alcohol by scatter plot but we have problem overploting and quality is integer we need spread point along x-axis, then I applied jitter function and transparing function alpha to solve these problem and after solve, I want to know the relationship between varibales then I make line smooth to know " as Alcohol increases the Quality increases"

### Plot Three
```{r echo=FALSE, Plot_Three}
ggplot(aes(x = quality, y= alcohol,color =density),data = whitewine)+
  scale_color_gradientn(colours = terrain.colors(4),guide = guide_legend(title = 'Density'))+
  geom_jitter(width = 1)+
  scale_y_continuous('Alcohol (% by volume)')+
  scale_x_continuous('Quality (score between 0 and 10)')+
  ggtitle('Quality vs Alcohol and Density')
```

### Description Three
This is the plot 2 but I add Density variable as color to see the relationship between three variables, the result I didn't show extremly relationship in this graph, because the color of density dependent on y variable "Alcohol" and indpendent on x variable "Quality".
------

# Reflection

> **Tip**: Here's the final step! Reflect on the exploration you performed and
the insights you found. What were some of the struggles that you went through?
What went well? What was surprising? Make sure you include an insight into
future work that could be done with the dataset.

> **Tip**: Don't forget to remove this, and the other **Tip** sections before
saving your final work and knitting the final report!